Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
fix bit about convergence with sharp edges

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 
triangles (density $1.11\times10^{-4}$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^{-5}$ $N/\text{\AA}$) 
triangles: the computed results show no discernible difference.

>>>>

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. 
We have completed grid-convergence analysis for this type of physics in a previous work, but using spherical geometries \cite{ClementiETal2019}. 
With that experience, and given the difficulty caused by sharp edges, we are satisfied with studying grid-independence here instead.
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
 to 19,200 triangles (density $1.11\times10^{-5}$ $\text{\AA}$ squared):
 the computed results show no discernible difference.
